### 2014-06-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update writeup

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters inside the structure. Therefore, the continued analysis will focus on the results of the baseline simulation results.

@@

@@

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161v}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS predicted temperature vectors, 1 second after interior door fails.}
\label{fig:temp_161v}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_165v}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature from baseline simulation, 15 seconds after interior door fails.}
\label{fig:temp_175s}
\end{figure}

\section{Pressure}

\begin{figure}[!ht]
\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres}
\input{../Scripts/colorbar_metric_pres}
\caption{FDS predicted pressure contours, 1 second prior to interior door failure.}
\label{fig:pres_159s}
\end{figure}

>>>>

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the interior conditions represented a significant hazard to firefighters inside the structure. Therefore, the analysis will focus on the results of the baseline simulation.

@@

\section{Pressure}
As the fire grows in the attic and back porch, the pressure rises. Fig.~(\ref{fig:pres_159s}) shows the pressure rise in the structure just before the interior door failed in the simulation. On the rear porch, the pressure rise ranges from a 4 Pa over pressure 1 m off the floor to greater than 10 Pa at the ceiling.
\begin{figure}[!ht]
\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres}
\input{../Scripts/colorbar_metric_pres}
\caption{FDS predicted pressure contours, 1 second prior to interior door failure.}
\label{fig:pres_159s}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature from baseline simulation, 15 seconds after interior door fails.}
\label{fig:temp_175s}
\end{figure}

From Fig.~(\ref{fig:temp_175s}), 15 seconds after the door failed, high temperature gases have descended to approximately 1 m (3.28 ft) off the ground through the interior hallway and have spilled into the kitchen (recall layout from Fig.~(\ref{fig:simp_geom})).
